\thispagestyle{empty}

\section*{Author's declaration}
\vspace*{1em}
Unless otherwise indicated in the text or references, or acknowledged above, this thesis is entirely the product of my own scholarly work. This thesis has not been submitted either in whole or part, for a degree at this or any other university or institution. This is to certify that the printed version is equivalent to the submitted electronic one.
\vspace{2em}\\
\abgabeort, \datumAbgabe
\vspace{3em}\\
\rule{6cm}{0.4pt}\\
\autor
\vspace*{1.5em}

\section*{License}

\vspace*{1.5em}
This work is licensed under a \acrfull{CCLicense}. It can be shared and adapted freely, as long as the original author receives appropriate credit. A link to the license is included, and changes are indicated. Commercial applications are not allowed and any work based on this document needs to be released under the same license. Detailed license information can be found at \url{http://creativecommons.org/licenses/by-nc-sa/4.0/}.
\vspace{1.5em}

\section*{Preliminary note}

\vspace*{1.5em}
Abbreviations or technical terms are not specially marked, but can be found in the list of abbreviations respectively in the glossary. While characterising or enumerating persons I will relinquish the feminine and just use the masculine form. This is because of simplification and should not be seen as any kind of discrimination. 

This document is referring to the code uploaded to the Git repository located at \url{github.com/steilerDev/myVerein}. The relevant commit has the short checksum \texttt{61538d} and was created on the 7\textsuperscript{th} of May 2015.
